Marlowe: financial contracts on blockchain\thanks{IOHK}

### 2018-05-16 tex/paper.tex
fixed path to .../pix/embedded.png
Adapt paper to LLNCS
Word-wrap source tex

\documentclass[
      acmsmall
    , screen
%    , authordraft
%    , anonymous
%    , review=true
  ]{acmart}

@@

% Copyright
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

@@

\citestyle{acmauthoryear}

@@

%%% FIXME PACKAGE SETUP %%%

\fxusetheme{color}
\fxuseenvlayout{color}

@@

% Title portion. Note the short title for running heads
\title
  [Marlowe]
  {Marlowe: financial contracts on blockchain}

\author{Pablo Lamela Seijas}
\affiliation{%
  \institution{University of Kent}
%  \streetaddress{School of Computing}
  \city{Canterbury}
  \state{Kent}
  \postcode{CT2 7NF}
  \country{UK}}
\email{pl292@kent.ac.uk}

\author{Simon Thompson}
\orcid{0000-0002-2350-301X}
\affiliation{%
  \institution{University of Kent}
%  \streetaddress{School of Computing}
  \city{Canterbury}
  \state{Kent}
  \postcode{CT2 7NF}
  \country{UK}}
\email{s.j.thompson@kent.ac.uk}

@@

This paper explores the design of a domain specific language, Marlowe,\footnote{Marlowe is named after Christopher Marlowe, the Elizabethan poet, dramatist and spy, who was born and educated in Canterbury, which is also where our university is based. \url{https://en.wikipedia.org/wiki/Christopher_Marlowe}}\footnote{The code for Marlowe is available from \url{https://github.com/input-output-hk/scdsl}
} targetted at the execution of financial contracts in the style of Peyton Jones, Eber and Seward~\cite{PeytonJones:2000} on blockchains. This work is a part of the Cardano project, and is supported by IOHK.\footnote{\url{https://iohk.io}}

@@

\begin{haskellcode}
data Contract =
   Null |
   CommitCash IdentCC Person Money Timeout Timeout Contract Contract |  
   RedeemCC IdentCC Contract |
   Pay IdentPay Person Person Money Timeout Contract |  
   Both Contract Contract |
   Choice Observation Contract Contract |
   When Observation Timeout Contract Contract   
   \end{haskellcode}
%Originally on "Choice": \footnote{Doesn't the step function need to record what observations are made, so they can be archived in the blockchain? I don't see how your design will support doing so.}\footnote{Yes, we assume that it is part of the infrastructure of this language to record the values of *observables* that are used. However, we have chosen no to make it part of the language itself.}

@@

Once the commitment \haskellinline{idCC} has expired and is redeemed, a \haskellinline{RedeemCC idCC k} contract will immediately evolve to \haskellinline{k}.
%\footnote{How does the contract determine what actions resulted from a given step? Or is this not required?}
%\footnote{If it is required, restructuring the DSL so that the result action appears as the 'value' of executing a step (using a monadic interface as described for id generation below) would be a good idea.}
%\footnote{We specify the actions generated by each kind of constructor; at each step the list of such actions, of type \haskellinline{AS}, is a component of the result.}.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=1\textwidth]{/home/palas/Escritorio/scdsl/tex/pix/embedded.png}
\par\end{centering}
\caption{\label{fig:embedded-demo}Screenshot of Meadow's embedded Fay editor.}
\end{figure}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

>>>>

\documentclass[runningheads]{llncs}

@@

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

@@

%\citestyle{acmauthoryear}

@@

@@

%
%
% Title portion. Note the short title for running heads
\title {Marlowe: financial contracts on blockchain\thanks{IOHK}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Pablo Lamela Seijas\orcidID{0000-0002-1730-1219}\\
\and Simon Thompson\orcidID{0000-0002-2350-301X}}
%
\authorrunning{P. Lamela Seijas and S. Thompson}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Kent, Canterbury, CT2 7NF, Kent (UK)}
\email{\{pl292,s.j.thompson\}@kent.ac.uk}

@@

This paper explores the design of a domain specific language, Marlowe,\footnote{Marlowe is named after Christopher 
Marlowe, the Elizabethan poet, dramatist and spy, who was born and educated in Canterbury, which is also where our 
university is based. \url{https://en.wikipedia.org/wiki/Christopher_Marlowe}}\footnote{The code for Marlowe is available 
from \url{https://github.com/input-output-hk/scdsl}} targetted at the execution of financial contracts in the style of 
Peyton Jones, Eber and Seward~\cite{PeytonJones:2000} on blockchains. This work is a part of the Cardano project, and is 
supported by IOHK.\footnote{\url{https://iohk.io}}

@@

\begin{haskellcode}
data Contract =
   Null |
   CommitCash IdentCC Person Money Timeout Timeout Contract Contract |  
   RedeemCC IdentCC Contract |
   Pay IdentPay Person Person Money Timeout Contract |  
   Both Contract Contract |
   Choice Observation Contract Contract |
   When Observation Timeout Contract Contract   
   \end{haskellcode}
%Originally on "Choice": \footnote{Doesn't the step function need to record what observations are made, so they can be 
%archived in the blockchain? I don't see how your design will support doing so.}\footnote{Yes, we assume that it is 
%part of the infrastructure of this language to record the values of *observables* that are used. However, we have 
%chosen no to make it part of the language itself.}

@@

Once the commitment \haskellinline{idCC} has expired and is redeemed, a \haskellinline{RedeemCC idCC k} contract will 
immediately evolve to \haskellinline{k}.
%\footnote{How does the contract determine what actions resulted from a given step? Or is this not required?}
%\footnote{If it is required, restructuring the DSL so that the result action appears as the 'value' of executing a 
%          step (using a monadic interface as described for id generation below) would be a good idea.}
%\footnote{We specify the actions generated by each kind of constructor; at each step the list of such actions, of type 
%          \haskellinline{AS}, is a component of the result.}.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=1\textwidth]{pix/embedded.png}
\par\end{centering}
\caption{\label{fig:embedded-demo}Screenshot of Meadow's embedded Fay editor.}
\end{figure}

@@

\bibliographystyle{splncs04}
\bibliography{paper}
